\center \fontsize{18}{20} \selectfont Revealing the Landscape of Globally Color-Dual Multi-loop Integrands

### 2023-12-04 notes/2loopNLSM/2loopNLSM.tex
tar ball for JHEP

Faced with this obstruction, we study the multi-loop sector of both
NLSM and Yang-Mills in \cref{2loopBoot} using an ansatz-based
color-dual bootstrap. In contrast to much of the available literature
on color-dual integrand construction at two-loop
\cite{Bern:2013yya,Mogull:2015adi,Johansson:2017bfl}, our results are
completely agnostic to the spacetime dimension; all the polarizations
and momenta appearing in our construction will remain formally
$D$-dimensional. This makes our methods and results particularly well
suited for algorithmically extracting rational terms from the
$D$-dependence of dimensionally regulated loop momenta.
The ansatz approach to constructing numerators generally results in an explosion of terms, but in the case of scalar theories there is an added difficulty because the linear equations become dense.
We were able overcome this barrier by employing a custom
solver, \texttt{FiniteFieldSolve}, which will soon be made
public.

@@

For a scalar theory like NLSM the numerator only depends on dot
products of momenta.  The basis of momentum invariants for both of the
graphs can be taken to be
\begin{equation}
\label{eq:scalar-basis}
N^{\text{NLSM}}\left[
  \scalebox{0.75}{\NLSMBasisDoubleBox} \right]
\text{ and }
N^{\text{NLSM}}\left[\scalebox{0.75}{\NLSMBasisPentaTriangle} \right]\in
\left\{\begin{array}{cccc}
    k_{13},& k_{23},& k_{15},& k_{16}, \\
    k_{25},& k_{26},& k_{35},& k_{36}, \\
    k_{55},& k_{56},& k_{66}
  \end{array}
  \right\},
\end{equation}
where $k_{ij}$ means $k_i \cdot k_j$, $k_5=\ell_1$, and $k_6 = \ell_2$.
Every vertex in NLSM scales as $k^2$ so the numerator of each diagram
scales as $k^{12}$.  At this mass dimension there are 8,008
independent dot products of momenta.  With two basis graphs there is a
total of 16,016 ansatz parameters.\footnote{\texttt{Mathematica} is
  not well suited for solving large sets of equations with sixteen thousand
  parameters, so a different method is desirable.  One possibility is
  to use a sparse solver, as often employed for integral reduction.
  However, these solvers typically assume that the matrix has a very
  low density.  While the equations in YM naturally separate into
  different ``helicity'' sectors (or $e_i \cdot e_j$ and
  $e_i \cdot k_j$ sectors in $D$ dimensions) which limits the
  cross-talk between equations and thus the effective density, there
  is no such separation of sectors in a scalar theory.  Thus the NLSM
  constraint equations were solved using a custom solver, working name
  \texttt{FiniteFieldSolve}, designed to exactly solve large linear
  systems of arbitrary density.  \texttt{FiniteFieldSolve} will be
  released publicly shortly.} Imposing the boundary Jacobi relations
eliminates all but 4,473 of the original free parameters.  Further
imposing graph symmetries reduces the number of free parameters to
1,243.

>>>>

Faced with this obstruction, we study the multi-loop sector of both
NLSM and Yang-Mills in \cref{2loopBoot} using an ansatz-based
color-dual bootstrap. In contrast to much of the available literature
on color-dual integrand construction at two-loop
\cite{Bern:2013yya,Mogull:2015adi,Johansson:2017bfl}, our results are
completely agnostic to the spacetime dimension; all the polarizations
and momenta appearing in our construction will remain formally
$D$-dimensional. This makes our methods and results particularly well
suited for algorithmically extracting rational terms from the
$D$-dependence of dimensionally regulated loop momenta.
The ansatz approach to constructing numerators generally results in an explosion of terms, but in the case of scalar theories there is an added difficulty because the linear equations become dense.
We were able overcome this barrier by employing a custom
solver, \texttt{FiniteFieldSolve} \cite{finitefieldsolve}.

@@

For a scalar theory like NLSM the numerator only depends on dot
products of momenta.  The basis of momentum invariants for both of the
graphs can be taken to be
\begin{equation}
\label{eq:scalar-basis}
N^{\text{NLSM}}\left[
  \scalebox{0.75}{\NLSMBasisDoubleBox} \right]
\text{ and }
N^{\text{NLSM}}\left[\scalebox{0.75}{\NLSMBasisPentaTriangle} \right]\in
\left\{\begin{array}{cccc}
    k_{13},& k_{23},& k_{15},& k_{16}, \\
    k_{25},& k_{26},& k_{35},& k_{36}, \\
    k_{55},& k_{56},& k_{66}
  \end{array}
  \right\},
\end{equation}
where $k_{ij}$ means $k_i \cdot k_j$, $k_5=\ell_1$, and $k_6 = \ell_2$.
Every vertex in NLSM scales as $k^2$ so the numerator of each diagram
scales as $k^{12}$.  At this mass dimension there are 8,008
independent dot products of momenta.  With two basis graphs there is a
total of 16,016 ansatz parameters.\footnote{\texttt{Mathematica} is
  not well suited for solving large sets of equations with sixteen thousand
  parameters, so a different method is desirable.  One possibility is
  to use a sparse solver, as often employed for integral reduction.
  However, these solvers typically assume that the matrix has a very
  low density.  While the equations in YM naturally separate into
  different ``helicity'' sectors (or $e_i \cdot e_j$ and
  $e_i \cdot k_j$ sectors in $D$ dimensions) which limits the
  cross-talk between equations and thus the effective density, there
  is no such separation of sectors in a scalar theory.  Thus the NLSM
  constraint equations were solved using a custom solver, 
  \texttt{FiniteFieldSolve}, designed to exactly solve large linear
  systems of arbitrary density \cite{finitefieldsolve}.} Imposing the boundary Jacobi relations
eliminates all but 4,473 of the original free parameters.  Further
imposing graph symmetries reduces the number of free parameters to
1,243.
